---
title: "Using the `powers` package"
author: "Vincenzo Coia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! If you need to perform a boxcos transformation to your fitted model you can do it with this package also!


```{r}
library(powers)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Want to apply the **boxcox** transformation to your linear model?

```{r}
fit <- lm(mpg ~ disp + drat + qsec , data=mtcars)
apply_boxcox(fit)
```

Now, you only need to take the transformed response for your linear regression

```{r}
mtcars$transformed_response <- apply_boxcox(fit)$transformed_response
head(mtcars)
new_fit <- lm(transformed_response ~ disp + drat +qsec , data=mtcars)
```

Furthermore, you can visualize the selected *lambda* for your transformation;

```{r}
transformation <- apply_boxcox(fit,plotit=TRUE)
```

Wow!!!
