---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for teaching purposes. 

# powers

This is an R package that gives `sqrt()` friends by providing other power functions. Moreover, you this package allow you to perform a *boxcox* transformation to linear model fitted by `lm()`. 

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hw07-CeciliaLe07/tree/master/powers-master")
```

## Example

See the vignette for more extensive use, but here are some examples:

```{r example_I}
powers::reciprocal(2)
```

```{r example_II}
powers::cube(10)
```

```{r example_III}
set.seed(548)
y <- rpois(20,5)
x <- rnorm(20)
powers::apply_boxcox(lm(y~x))
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, and `reciprocal`. 
